% \section{2019 - Loc Hinh}
    \section{On the Use of Cloud and Semantic WebTechnologies for Generative Design}

    % \url{https://pdfs.semanticscholar.org/cb19/48180388287ffe17d843f6e2d2e1fb5de46e.pdf}
    % \bigskip 
    
    % \subsubsection*{What is the problem being solved}
    Generative Design is a new programming paradigm often used in AutoCAD. Data sources that are different and similar, validation processes and optimizing knowledge base, and storing and managing Generative Design artifacts.
    Utilize Cloud for data sourcing for certain Autocad simulations, processing of simple and complex validation of Generative Design artifacts, and storing and managing Generative Design artifacts.
    Three points to address: data sources, validating artifacts and storing, managing, indexing artifacts. Data sources are hosted on the Cloud and similarities between sources are grouped without disturbing the original source format. Artifact verification is done in two steps: first they perform simple validation locally and complex validation using Cloud processing; second they indexed their validation sources similarly to their data sources to enable reuse. Storing and managing artifacts are in progress, but suggests that using metadata to locate files stored on the Cloud, artifacts can be stored anywhere compared to the classic method of maintaining artifact relationships.

    \section{Business Driven Insight via a Schema-Centric DataFabric}

    % \url{http://ceur-ws.org/Vol-2456/paper80.pdf}
    % \bigskip 
    
    Analytics and Business Intelligence (BI) tools are not successful due to difficulty understanding both where the data came from and what the data means.
    Using ‘schema centric data fabric’ to model business structures allows the businesses to easily choose and send their data to analytic tools. Any generated data from analytic tools will retain context as the data conforms to the schema. 
    AWS’ Neptune offers high data availability, guaranteed transactions performing parallel updates, and light analytics processing. This service allows all data from the ‘schema centric data fabric’ to be stored on Neptune, and manipulated all within that service for light analytics. Creating and managing more complex analytics will require some custom components and user interfaces to be written, while utilizing SHACL to communicate between cloud applications. Modeling the business is done using RDF/OWL.

